### 2022-09-06 paper/sections/numerical.tex
Fix typo in Dehnen formula
Begin writing a bit on HMC
- update some figures using the new analysis methods
Switch to MNRAS template
- Discuss more about statistical implementation

- Change project name from Himmel

@@

We create four\footnote{A fifth galaxy, model B, was created with much higher mass than the four presented here. As the merger system did not result in a bound SMBH binary within some $10\,\text{Gyr}$, we exclude discussion of this galaxy.} unique progenitor galaxies, motivated by analogues observed in the real Universe. 
Each galaxy is modelled as a multi-component system: a stellar component embedded within a DM halo, and a single SMBH at rest at the centre of the galaxy. 
Two galaxies, A and D, have a stellar density profile given by the `cuspy' \citet{dehnen93} profile:
\begin{equation}\label{eq:dehnen}
    \rho_\star(r) = \frac{M_\star}{2\pi} \frac{a}{r(r+a)^{(4-\gamma)}}
\end{equation}
and two galaxies, C and E, by the `cored' \citet{terzic05} profile:
\begin{align}\label{eq:terzic}
    \rho_\star(r) &= \rho' \left[ 1+\left(\frac{r_b}{r} \right)^\alpha \right]^{\gamma/\alpha} \\
    &\times \left\{ \left[ \frac{r^\alpha+r_b^\alpha}{R_\text{e}^\alpha} \right]^{-p/\alpha} \text{e}^{-b \left[ \left(r^\alpha+r_b^\alpha\right)/R_\text{e}^\alpha \right]^{1/n\alpha}} \right\}, \nonumber
\end{align}
where
\begin{equation}
    \rho' = \rho_b 2^{(p-\gamma)/\alpha} \left(\frac{r_b}{r} \right)^p \text{e}^{b\left(2^{1/\alpha r_b/R_\text{e}}\right)^{1/n}}.
\end{equation}

@@

Conversely, the DM halo of all galaxies is modelled as an ergodic Navarro-Frenk-White (NFW) profile \citep{navarro97}, with expected virial mass taken from the \citet{behroozi19} peak halo mass -- stellar mass relation. 
\begin{equation}\label{eq:nfw}
    \rho_\text{DM}(r) = \frac{\rho_0}{(r/a)(1+r/a)^2}
\end{equation}
We do not incorporate a redshift-dependent halo mass, instead opting to model our haloes as if they were taken at $z=0$. 
The NFW concentration parameter $c\equiv r_\text{vir}/a$, where $a$ is the scale radius, is taken from the \citet{dutton14} relation.
To prevent the radially-divergent mass distribution associated with the NFW profile, we multiply the density profile \eqref{eq:nfw} with a sigmoid function, and demand that the ratio of the actual DM density to the theoretical NFW density satisfies
\begin{equation*}
    \frac{\rho_\text{true}(r)}{\rho_\text{NFW}(r)} < 10^{-5}
\end{equation*}
by $7\,R_\text{vir}$, with significant departure from the NFW profile already by $3\,R_\text{vir}$. 
With this modified NFW profile, the phase space is Monte Carlo sampled using the approach of \eqref{eq:om} and a minimum of $\sim10^6$ particles with a mass of $3.0\times10^7\,\text{M}_\odot$, assuming $L=0$ and $r_a\rightarrow\infty$. 
The virial radius of the system is then re-determined numerically, to ensure it is in close agreement with the expected value from \citet{behroozi19}.

The final component of the model galaxies, the SMBH, is represented as a point mass at rest at the origin. 
The SMBH mass is taken from the $M_\text{bulge}\text{--}M_\bullet$ relation of \citet{sahu19}, and by definition lies on this relation. 
The SMBH is also given an initial spin $\chi$ from the \citet{lousto10} distribution, so that we may also investigate GW-induced recoil kicks in our merger remnants.

After creating the multicomponent ICs, the galaxies are evolved in isolation using \gadget for at least \drafting{$8\,\text{Gyr}$}, to ensure the systems are fully-relaxed and any potential effects arising from radial instabilities are mitigated. 
We then extract the evolved systems, and align each system with its reduced inertia tensor.
We use these as the progenitor galaxies for all subsequent merger configurations.

\begin{deluxetable*}{cccccccccc}
    \tablecaption{
        Properties of Progenitor Galaxies
    }
    \tablehead{
        \colhead{Name} &
        \colhead{Stellar Profile} &
        \colhead{$r_a/\text{kpc}$} &
        \colhead{$M_\star/10^{11}\,\text{M}_\odot$} &
        \colhead{$N_\star$} &
        \colhead{$M_\text{DM}/10^{13}\,\text{M}_\odot$} &
        \colhead{$c_\text{DM}$} &
        \colhead{$N_\text{DM}$} &
        \colhead{$M_\bullet/10^{9}\,\text{M}_\odot$} &
        \colhead{$R_\text{vir}/\text{kpc}$}
    }
    \startdata
        A & Dehnen & 0.4 & 2.51 & $2.5\times10^6$ & 9.65 & 7.55 & $3.22\times10^6$ & 3.04 & 554
        \\
        C & Terzi\'c & 1.5 & 2.57 & $2.6\times10^6$ & 5.13 & 7.51 & $3.38\times10^6$ & 3.14 & 562
        \\
        D & Dehnen & 0.3 & 1.58 & $1.58\times10^6$ & 2.00 & 8.23 & $1.29\times10^6$ & 1.64 & 412
        \\
        E & Terzi\'c & 0.5 & 1.46 & $1.46\times10^6$ & 3.29 & 8.36 & $1.10\times10^6$ & 1.46 & 392
    \enddata
    \end{deluxetable*}

@@

We simulate all 6 different progenitor combinations, namely AC, AD, AE, CD, CE, DE. 
This allows us to sample a vast range of progenitor configurations: each of equal and unequal mass, for each combination of cuspy and cored profiles.

In keeping with our theme of realistic initial conditions, we set all galaxy merger orbits to an initial separation of $r_0=3\,R_\text{vir,1}$, where $R_\text{vir,1}$ is the virial radius of the larger of the two progenitors. 
The progenitor galaxies are then set on a quasi-Keplerian orbit, assuming each galaxy is a point-mass containing half its total mass. 
The eccentricity of the initial orbit is chosen as a function of the initial pericentre distance $r_\text{peri}$, motivated from cosmological simulations, using the data presented in \citet{khochfar06}.
By fitting a functional form to the median eccentricity value in logarithmically-spaced bins, we arrive at the relation
\begin{equation}\label{eq:rperi-e}
    e(r_\text{peri}/R_\text{vir,1}) = \left[ 1 + \left( \frac{r_\text{peri}/R_\text{vir,1}}{0.320} \right)^{1.629} \right]^{-0.176}
\end{equation}
from which we set the initial eccentricity of all our merger orbits.
For each progenitor combination, we sample six different pericentre distances, and thus six different eccentricities, in the range $10^{-3} \leq r_\text{peri}/R_\text{vir,1} \leq 1.0$.

@@

The progenitors are evolved through the \textit{parent phase} from $t(r_0)=0$ with \gadget until the SMBHs form a bound binary at $t_\text{stop}$, with a stellar softening of $\epsilon_\star=10\,\text{pc}$ and \gadget integration tolerances \texttt{ErrTolIntAccuracy}=$0.02$ and \texttt{ErrTolForceAcc}=$0.005$.
We then initialise the \textit{child phase} by restarting from a snapshot sometime before $t_\text{stop}$.
We apply a small perturbation to each SMBH position and velocity vector to mimic the effect of Brownian motion due to discrete sampling of the DF, thus negating the need to run many simulations from $r_0=3\,R_\text{vir,1}$. 
The perturbations are drawn from a Gaussian distribution modelling the typical offset of the SMBH phase space coordinates from the phase space coordinates of the stellar centre of mass, determined using the shrinking sphere method. 
The Gaussian distributions are characterised by $\mathcal{N}_\text{pos}\sim(\mu=0\,\text{pc}, \sigma^2=100\,\text{pc}^2)$, and $\mathcal{N}_\text{vel}\sim(\mu=0\,\text{km\,s}^{-1}, \sigma^2=100\,\text{km}^2\text{\,s}^{-2})$ for each progenitor \drafting{should we show a figure of this?}. 
From each \parent, we create ten uniquely-perturbed \child runs, allowing us to explore the distribution of parameters describing both the orbital and remnant properties of each \parent merger. 
Additionally, we lower the stellar softening to $\epsilon_\star=3.5\,\text{pc}$ and tighten the integration tolerance \texttt{ErrTolIntAccuracy} to $0.002$ to optimise the run for \ketju.
We check for energy conservation between the \parent and \child runs, and confirm that the total energy is conserved at the sub-percent level. 
In total, we perform 360 ultra-high resolution unique \child simulations using \ketju, and use this sample for our analysis.

@@

\begin{deluxetable*}{ccc}
\tablecaption{
    Properties of Merger Orbits
}
\tablehead{
    \colhead{Name} &
    \colhead{$r_\text{peri}/R_\text{vir,1}$} &
    \colhead{$e_0$} 
}
\startdata
    XY-030-0001 & $1.0\times10^{-3}$ & 0.999
    \\
    XY-030-0005 & $5.0\times10^{-3}$ & 0.998
    \\
    XY-030-0010 & $1.0\times10^{-2}$ & 0.994
    \\
    XY-030-0050 & $5.0\times10^{-2}$ & 0.992
    \\
    XY-030-0100 & $1.0\times10^{-1}$ & 0.976
    \\
    XY-030-1000 & $1.0\times10^{-0}$ & 0.703
\enddata
\end{deluxetable*}

\subsection{Bayesian Hierarchical Modelling}
\drafting{\begin{enumerate}
    \item HMC algorithm?
    \item Description of hierarchical model
    \item Prior distributions
    \item forward modelling
\end{enumerate}
}

\begin{figure*}
    \centering
    \includegraphics{compic.png}
    \caption{\drafting{some key IC plots}}
    \label{fig:ics}
\end{figure*}

\begin{figure*}
    \centering
    \includegraphics[width=0.5\textwidth]{initial_orbits.jpeg}
    \caption{\drafting{Plots of the initial orbit?}}
    \label{fig:icorbit}
\end{figure*}

>>>>

\begin{table*}
    \centering
    \caption{Properties of progenitor galaxies}
    \label{tab:ics}
    \begin{tabular}{ccccccccccc}
        \hline
        Name & Stellar Profile & $r_a/\text{kpc}$ & $M_\star/(10^{11}\,\Msun)$ & $N_\star$ & $M_\text{DM}/(10^{13}\,\Msun)$ & $c_\text{DM}$ & $N_\text{DM}$ & $M_\bullet/(10^{9}\,\Msun)$ & $R_\text{vir}/\mathrm{kpc}$ & $R_\mathrm{e}/\mathrm{kpc}$ \\
        \hline
        A & Dehnen & 0.4 & 2.51 & $2.5\times10^6$ & 9.65 & 7.55 & $3.22\times10^6$ & 3.04 & 554 & 4.40 \\
        C & Terzi\'c & 1.5 & 2.57 & $2.6\times10^6$ & 5.13 & 7.51 & $3.38\times10^6$ & 3.14 & 562 & 4.05 \\
        D & Dehnen & 0.3 & 1.58 & $1.58\times10^6$ & 2.00 & 8.23 & $1.29\times10^6$ & 1.64 & 412 & 3.16 \\
        E & Terzi\'c & 0.5 & 1.46 & $1.46\times10^6$ & 3.29 & 8.36 & $1.10\times10^6$ & 1.46 & 392 & 2.79 \\
        \hline
    \end{tabular}
\end{table*}

@@

\begin{figure*}
    \centering
    \includegraphics{compic.pdf}
    \caption{\drafting{Comparison of progenitor galaxies to key observables. \textit{Left:} The simulated galaxies have a SMBH mass determined from the \citet{sahu19} relation. Cored galaxies are shown as circles, and cuspy galaxies as squares. Note the progenitor galaxies A and C overlap. \textit{Centre}: The stellar velocity dispersion within $1\,R_\mathrm{e}$ is computed for the progenitor galaxies, and compared to observational data collated in \citet{bosch16}. \textit{Right:} The dark matter fraction within $1\,R_\mathrm{e}$ is computed for the progenitor galaxies, and compared to Schwarzschild-modelling results from \citet{jin20}.}}
    \label{fig:ics}
\end{figure*}

We create four\footnote{A fifth galaxy, model B, was created with much higher mass than the four presented here. As the merger system did not result in a bound SMBH binary within some $10\,\text{Gyr}$, we exclude discussion of this galaxy.} unique progenitor galaxies, motivated by analogues observed in the real Universe. 
Each galaxy is modelled as a multi-component system: a stellar component embedded within a DM halo, and a single SMBH at rest at the centre of the galaxy. 
Two galaxies, A and D, have a stellar density profile given by the `cuspy' \citet{dehnen93} profile:
\begin{equation}\label{eq:dehnen}
    \rho_\star(r) = \frac{(3-\gamma)M_\star}{4\pi} \frac{a}{r^\gamma (r+a)^{(4-\gamma)}}
\end{equation}
and two galaxies, C and E, by the `cored' \citet{terzic05} profile:
\begin{align}\label{eq:terzic}
    \rho_\star(r) &= \rho' \left[ 1+\left(\frac{r_b}{r} \right)^\alpha \right]^{\gamma/\alpha} \\
    &\times \left\{ \left[ \frac{r^\alpha+r_b^\alpha}{R_\text{e}^\alpha} \right]^{-p/\alpha} \text{e}^{-b \left[ \left(r^\alpha+r_b^\alpha\right)/R_\text{e}^\alpha \right]^{1/n\alpha}} \right\}, \nonumber
\end{align}
where
\begin{equation}
    \rho' = \rho_b 2^{(p-\gamma)/\alpha} \left(\frac{r_b}{r} \right)^p \text{e}^{b\left(2^{1/\alpha r_b/R_\text{e}}\right)^{1/n}}.
\end{equation}

@@

Conversely, the DM halo of all galaxies is modelled as an ergodic Navarro-Frenk-White (NFW) profile \citep{navarro97}, with expected virial mass taken from the \citet{behroozi19} peak halo mass -- stellar mass relation. 
\begin{equation}\label{eq:nfw}
    \rho_\text{DM}(r) = \frac{\rho_0}{(r/a)(1+r/a)^2}
\end{equation}
We do not incorporate a redshift-dependent halo mass, instead opting to model our haloes as if they were taken at $z=0$. 
The NFW concentration parameter $c\equiv r_\text{vir}/a$, where $a$ is the scale radius, is taken from the \citet{dutton14} relation.
To prevent the radially-divergent mass distribution associated with the NFW profile, we multiply the density profile \autoref{eq:nfw} with a sigmoid function, and demand that the ratio of the actual DM density to the theoretical NFW density satisfies
\begin{equation*}
    \frac{\rho_\text{true}(r)}{\rho_\text{NFW}(r)} < 10^{-5}
\end{equation*}
by $7\,R_\text{vir}$, with significant departure from the NFW profile already by $3\,R_\text{vir}$. 
With this modified NFW profile, the phase space is Monte Carlo sampled using the approach of \autoref{eq:om} and a minimum of $\sim10^6$ particles with a mass of $3.0\times10^7\,\text{M}_\odot$, assuming $L=0$ and $r_a\rightarrow\infty$. 
The virial radius of the system is then re-determined numerically, to ensure it is in close agreement with the expected value from \citet{behroozi19}.

The final component of the model galaxies, the SMBH, is represented as a point mass at rest at the origin. 
The SMBH mass is taken from the $M_\text{bulge}\text{--}M_\bullet$ relation of \citet{sahu19}, and by definition lies on this relation, shown in the left panel of \autoref{fig:ics}. 
The SMBH is also given an initial spin $\chi$ from the \citet{lousto10} distribution, so that we may also investigate GW-induced recoil kicks in our merger remnants.

We compare the progenitor systems to key constraining observables in \autoref{fig:ics}.
In the centre panel, we overlay our progenitor galaxies on data used to fit the black hole mass - central stellar velocity dispersion relation of \citet{bosch16}. 
The progenitor galaxies lie within the spread of the data, and have velocity dispersions indistinguishable from observational data. 
Similarly, we find that the fraction of dark matter within $1\,R_\mathrm{e}$ is comparable to the dark matter fraction determined with Schwarzschild modelling of central and satellite galaxies in the MaNGA survey \citep{jin20}, shown in the right panel of \autoref{fig:ics}.
Our progenitor galaxies are consistently slightly below the median relation (the median $f_\mathrm{DM}$ value is shown as crosses in stellar mass bins), but still well within the scatter of \citet{jin20}. 
We conclude that our progenitor galaxy models, whilst neglecting the inclusion of gas, plausibly represent observable massive galaxies, particularly at the mass range of $M_\star/\Msun > 10^{11}$ that we are interested in.

After creating and assessing the multicomponent ICs, the galaxies are evolved in isolation using \gadget for at least \drafting{$8\,\text{Gyr}$}, to ensure the systems are fully-relaxed and any potential effects arising from radial instabilities are mitigated. 
We then extract the evolved systems, and align each system with its reduced inertia tensor.
We use these as the progenitor galaxies for all subsequent merger configurations.

@@

We simulate all six different progenitor combinations, namely AC, AD, AE, CD, CE, DE. 
This allows us to sample a vast range of progenitor configurations: each of equal and unequal mass, for each combination of cuspy and cored profiles. 
Herein, we refer to a particular progenitor combination as a \textit{progenitor class}.

In keeping with our theme of realistic initial conditions, we set all galaxy merger orbits to an initial separation of $r_0=3\,R_\text{vir,1}$, where $R_\text{vir,1}$ is the virial radius of the larger of the two progenitors. 
The progenitor galaxies are then set on a quasi-Keplerian orbit, assuming each galaxy is a point-mass containing half its total mass. 
The eccentricity of the initial orbit is chosen as a function of the initial pericentre distance $r_\text{peri}$, motivated from cosmological simulations, using the data presented in \citet{khochfar06}.
By fitting a functional form to the median eccentricity value in logarithmically-spaced bins, we arrive at the relation
\begin{equation}\label{eq:rperi-e}
    e(r_\text{peri}/R_\text{vir,1}) = \left[ 1 + \left( \frac{r_\text{peri}/R_\text{vir,1}}{0.320} \right)^{1.629} \right]^{-0.176}
\end{equation}
from which we set the initial eccentricity of all our merger orbits.
For each progenitor class, we sample six different pericentre distances, and thus six different eccentricities, in the range $10^{-3} \leq r_\text{peri}/R_\text{vir,1} \leq 1.0$. 
Consequently, we investigate 36 `families' of merger configurations.

@@

The progenitors are evolved through the \textit{parent phase} from $t(r_0)=0$ with \gadget until the SMBHs form a bound binary at $t_\text{stop}$, with a stellar softening of $\epsilon_\star=10\,\text{pc}$ and \gadget integration tolerances \texttt{ErrTolIntAccuracy}=$0.02$ and \texttt{ErrTolForceAcc}=$0.005$.
We then initialise the \textit{child phase} by restarting from a snapshot sometime before $t_\text{stop}$.
We apply a small perturbation to each SMBH position and velocity vector to mimic the effect of Brownian motion due to discrete sampling of the DF, thus negating the need to run many simulations from $r_0=3\,R_\text{vir,1}$. 
The perturbations are drawn from a Gaussian distribution modelling the typical offset of the SMBH phase space coordinates from the phase space coordinates of the stellar centre of mass, determined using the shrinking sphere method. 
The Gaussian distributions are characterised by $\mathcal{N}_\text{pos}(\mu=0\,\text{pc}, \sigma^2=100\,\text{pc}^2)$, and $\mathcal{N}_\text{vel}(\mu=0\,\text{km\,s}^{-1}, \sigma^2=100\,\text{km}^2\text{\,s}^{-2})$ for each progenitor \drafting{should we show a figure of this?}. 
From each \parent, we create ten uniquely-perturbed \child runs, allowing us to explore the distribution of parameters describing both the orbital and remnant properties of each \parent merger. 
Additionally, we lower the stellar softening to $\epsilon_\star=3.5\,\text{pc}$ and tighten the integration tolerance \texttt{ErrTolIntAccuracy} to $0.002$ to optimise the run for \ketju.
We check for energy conservation between the \parent and \child runs, and confirm that the total energy is conserved at the sub-percent level. 
In total, we perform 360 ultra-high resolution unique \child simulations using \ketju, and use this sample for our analysis.

@@

\begin{table}[t]
    \centering
    \caption{Properties of merger orbits}
    \label{tab:mergers}
    \begin{tabular}{ccc}
        \hline
        Name & $r_\text{peri}/R_\text{vir,1}$ & $e_0$ \\
        \hline
        XY-030-0001 & $1.0\times10^{-3}$ & 0.999 \\
        XY-030-0005 & $5.0\times10^{-3}$ & 0.998 \\
        XY-030-0010 & $1.0\times10^{-2}$ & 0.994 \\
        XY-030-0050 & $5.0\times10^{-2}$ & 0.992 \\
        XY-030-0100 & $1.0\times10^{-1}$ & 0.976 \\
        XY-030-1000 & $1.0\times10^{0}$ & 0.703 \\
        \hline
    \end{tabular}
\end{table}

\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{initial_orbits.jpeg}
    \caption{\drafting{Plots of the initial orbit? Update this figure if so}}
    \label{fig:icorbit}
\end{figure}

### 2022-09-06 paper/sections/results.tex
Switch to MNRAS template
- Discuss more about statistical implementation

- Change project name from Himmel

\drafting{
Figures to do
\begin{itemize}
\item Example of forward-modelled semimajor axis and eccentricity
\item Example of forward-modelled density profile
\item Example of forward-modelled velocity dispersion profile
\end{itemize}
Table of galaxy properties,
and maybe another one of BH merger remnant properties.
}

@@

\begin{figure*}
    \includegraphics[width=\textwidth]{{graham_density-A-C-3.0-0.05_prior_pred_log10_proj_density_mean}.png}
    \caption{\drafting{Prior predictive estimate for the core-S\'ersic fit. Darker shaded regions correspond to higher Bayesian Credible Intervals (BCIs). The observed data is overlaid. From the prior predictive estimate, it is seen that the model and the assumed parameter hyperdistributions are able to describe the observed data, in that the observed data lies within the range allowed by the prior predictive estimate.}}
    \label{fig:priorpred}
\end{figure*}
\begin{figure*}
    \includegraphics[width=0.7\textwidth]{{graham_density-A-C-3.0-0.05_pair_0}.png}
    \caption{\drafting{Corner plot of hierarchical model hyperparameters. Each of the hyperdistributions are modelled as Gamma distributions with shape parameters $\alpha$ and $\beta$. For example, the hyperdistribution on the core radius $r_\mathrm{b}$ is modelled as $r_\mathrm{b} \sim \text{Gamma}(r_{\mathrm{b},\alpha}, r_{\mathrm{b},\beta})$. Critically, the hyperdistributions are unimodal with highest-density regions located some distance from the distribution edges, indicating the HMC sampling has converged well. }}
    \label{fig:corner_params_1}
\end{figure*}
\begin{figure*}
    \includegraphics[width=0.7\textwidth]{{graham_density-A-C-3.0-0.05_pair_1}.png}
    \caption{\drafting{Same as \ref{fig:corner_params_1}}}
    \label{fig:corner_params_2}
\end{figure*}
\begin{figure*}
    \includegraphics[width=0.7\textwidth]{{graham_density-A-C-3.0-0.05_posterior_pred_log10_proj_density_mean}.png}
    \caption{\drafting{Posterior predictive estimate for the core-S\'ersic fit. Darker shaded regions correspond to higher Bayesian Credible Intervals (BCIs). The observed data is overlaid, and seen to lie well within the 50\% BCI. }}
    \label{fig:postpred}
\end{figure*}

%\begin{figure*}
%\includegraphics{binary_params_main}
%\includegraphics{binary_params_secondary}
%\includegraphics{binary_params_tertiary}
%\caption{
%\drafting{
%Binary orbital parameters. Dashed line for triplet outer orbit (dashes not very %visible at the moment).
%Lower panels are mergers occurring in separate galaxies.
%Note the use of $1-e$ for the last panel.
%}
%}
%\label{fig:binary_params}
%\end{figure*}

>>>>

\drafting{
Figures to do
\begin{itemize}
\item Example of forward-modelled semimajor axis and eccentricity
\item Example of forward-modelled density profile
\item Example of forward-modelled velocity dispersion profile
\end{itemize}
and maybe another one of BH merger remnant properties.
}

@@

\drafting{ENSURE CONSISTENCY WITH SIGMA AND I. AS WE ARE USING MASS DENSITY, SHOULD BE SIGMA, NOT I, OR ASSUME A M/L RATIO OF 1. NEED TO GO THROUGH AND ENSURE THIS}

\subsection{Projected Mass Density Profiles}
We use hierarchical modelling to recover the population parameter distributions of the core-S\'ersic model \autoref{eq:coresersic} for each simulation family. 
We enforce a sharp transition from the core to outer galaxy regions by setting $\alpha$ in \autoref{eq:coresersic} to 10.0. 
A probabilistic graphical model detailing the connection between hyperparameters, latent parameters, and observables is given in \autoref{fig:graphicalmodel}.

\begin{table}
    \centering
    \caption{The parameters for each hyperparameter distribution for the core-S\'ersic model, where each distribution is a gamma distribution.}
    \label{tab:cshypers}
    \begin{tabular}{ccc}
        \hline
        Hyperparameter & $\alpha$ & $\beta$ \\
        \hline
        $r_{\mathrm{b}, \alpha}$ & 3.0 & 2.0 \\
        $r_{\mathrm{b}, \beta}$ & 10.0 & 8.0 \\
        $R_{\mathrm{e}, \alpha}$ & 30.0 & 2.0 \\
        $R_{\mathrm{e}, \beta}$ & 40.0 & 2.0 \\
        $\tilde{\Sigma}_{\mathrm{b}, \alpha}$ & 20.0 & 4.0 \\
        $\tilde{\Sigma}_{\mathrm{b}, \beta}$ & 20.0 & 2.0 \\
        $\gamma_\alpha$ & 1.0 & 2.0 \\
        $\gamma_\beta$ & 4.0 & 2.0 \\
        $n_\alpha$ & 16.0 & 2.0 \\
        $n_\beta$ & 4.0 & 2.0 \\
        \hline
    \end{tabular}
\end{table}

\begin{figure}
    \includegraphics{hm_coresersic.pdf}
    \caption{Probabilistic graphical model for the likelihood of the core-S\'ersic model. Probabilistic parameters and observable quantities (hatted variables) are shown as circles, whereas deterministic quantities are represented by diamonds. Hyperparameters are represented by purple circles, latent parameters in blue, and observable quantities as red circles. The nodes indicate the distribution used in constructing the prior distributions (for latent parameters) and likelihood function (for $\hat{\Sigma}$). The radial box represents observed and latent variables for each radial bin for a \child, and the child box represents latent parameters for each \child simulation in a family. }
    \label{fig:graphicalmodel}
\end{figure}

\subsubsection{Observable Quantities}
The hierarchical model takes three observable quantities, denoted by hat-variables in red circles in \autoref{fig:graphicalmodel}. 
These variables are the radius $\hat{R}$, and the mean projected mass density $\hat{\Sigma}$, and the standard deviation of the projected mass density $\hat{\sigma}_\Sigma$ measured in the radial bins centred on $\hat{R}$.
For each \child simulation, we choose to `observe' the first snapshot where the binary semimajor axis is \textit{at most} $10\,\mathrm{pc}$. 
In the event that there is no snapshot satisfying the above requirement (due to, for example, rapid merging of the SMBH binary in a time period shorter than the snapshot output frequency), the \child simulation is not included in the analysis.
We enforce a minimum of six \child simulations per family for that family to be analysed with our hierarchical modelling technique. 
For those \child simulations which pass our selection criteria, we take 30 random projections of the merger remnant, and determine the projected mass density in 50 radial bins evenly-spaced in logarithm space, with a minimum value of $0.2\,\mathrm{kpc}$ and a maximum value of $20.0\,\mathrm{kpc}$.
This allows us to build up a distribution of projected mass densities per radial bin, from which $\hat{\Sigma}$ and $\hat{\sigma}_\Sigma$ are determined.

\subsubsection{Latent Parameters for Observables}
With the omission of the parameter $\alpha$ in the modelling process, there are five latent parameters ($r_\mathrm{b}$, $R_\mathrm{e}$, $\tilde{\Sigma}_\mathrm{b}$, $\gamma$, and $n$, the set of which we denote as $\kappa$) that describe each \child simulation in a family. 
Here, we define $\tilde{\Sigma}_\mathrm{b} \equiv \Sigma_\mathrm{b}/10^{10}$, where $\Sigma_\mathrm{b}$ is defined in \autoref{eq:coresersic2}.
These latent parameters, depicted as non-hatted variables in blue circles in \autoref{fig:graphicalmodel}, are sampled to obtain a latent estimate on the projected mass density, $\Sigma$.
As each latent parameter in the set $\kappa$ is strictly non-negative, we use as prior distributions for each latent parameter a gamma distribution with hyperparameters $(\kappa_\alpha, \kappa_\beta)$, which are themselves drawn from a gamma distribution. 
To ensure our hyperparameter prior distributions are weakly-informative, the hyperparameters are drawn from the distributions in \autoref{tab:cshypers} for all simulation families. 
The sampled hyperparameter distributions are shown as corner plots in Figures \ref{fig:corner_params_1}-\ref{fig:corner_params_3}.

We ensure our hyperparameter and latent parameter distributions are representative of our observed data by performing prior predictive checks, an example of which is shown for the A-C-3.0-0.05 family in \autoref{fig:priorpred}. 
Critically, both the range of values spanned by the prior distributions and the general shape of the distribution suggests that the data is well represented by the model and the prior distributions on the hyper and latent parameters.

As likelihood function, we use the lognormal distribution $\mathrm{Lognorm}(\Sigma, \hat{\sigma}_\Sigma^2)$ as it a) has support on $[0,\infty)$, and b) produces normally-distributed variates in logarithm space, which is representative of the distribution of $\hat{\Sigma}$ for a given radial bin when we backwards-model and na\"ively bin our observations of $\hat{\Sigma}$ for that radial bin.

\drafting{Write explicitly the posterior distribution we are sampling from.}

\subsection{Latent Parameter Posterior Distributions}
We compute the posterior distribution using \textsc{Stan}, ensuring that the sampler exits without encountering any divergences, and that all \drafting{R-hat (is a summary stat, but how to draw? Don't want to confuse with observed radius)} values are within the range \drafting{$[0.99, 1.01]$}.
We first inspect how the posterior distribution appears visually by computing posterior predictive checks, an example of which is shown in \autoref{fig:postpred} for the family A-C-3.0-0.05. 
We find that the data is well described by the 50\% BCI \drafting{introduce what BCI is} of the posterior distribution, as desired.

As part of the hierarchical modelling sampling process, we obtain in addition to the posterior distribution on $\Sigma(R)$ the latent parameter distributions from which $\Sigma(R)$ is determined. 
We compare the latent parameter distributions in \autoref{fig:compareAC} for the AC merger class\footnote{The merger family A-C-3.0-1.0 did not have enough \child samples (3 from 10) from which to construct the likelihood function, and thus is omitted here.}, with line colour corresponding to the first pericentre distance of the merger family, $r_\mathrm{peri}/R_{\mathrm{vir},1}$. 
We find no convincing evidence for an influence of first pericentre distance on the resulting projected mass density profiles, with the distributions of latent parameters consistent between all families in the AC progenitor class. 
Whilst we purposely avoid point estimates on our latent parameter distributions, we report the median values here to give a sense of scale. 
For the AC progenitor class, we find the core radius to be $\sim 1.4\,\mathrm{kpc}$, effective radius $\sim 7.2\,\mathrm{kpc}$ (recall progenitor A had $R_\mathrm{e} \sim 4\,\mathrm{kpc}$), normalising density of $\sim 3.1\times10^9\,\Msun\,\mathrm{kpc}^{-2}$, core slope index of $\sim 0.05$, and S\'ersic index of $\sim 1.8$.

\drafting{
    \begin{itemize}
        \item corner plot description
        \item comparison between rperi values, maybe new section?
    \end{itemize}
}

\begin{figure*}
    \includegraphics[width=\textwidth]{{graham_density-A-C-3.0-0.05_prior_pred_log10_proj_density_mean}.png}
    \caption{\drafting{Prior predictive estimate for the core-S\'ersic fit. Darker shaded regions correspond to higher Bayesian Credible Intervals (BCIs). The observed data is overlaid. From the prior predictive estimate, it is seen that the model and the assumed parameter hyperdistributions are able to describe the observed data, in that the observed data lies within the range allowed by the prior predictive estimate.}}
    \label{fig:priorpred}
\end{figure*}

\begin{figure*}
    \includegraphics[width=0.7\textwidth]{{graham_density-A-C-3.0-0.05_pair_0}.png}
    \caption{\drafting{Corner plot of hierarchical model hyperparameters. Each of the hyperdistributions are modelled as Gamma distributions with shape parameters $\alpha$ and $\beta$. For example, the hyperdistribution on the core radius $r_\mathrm{b}$ is modelled as $r_\mathrm{b} \sim \text{Gamma}(r_{\mathrm{b},\alpha}, r_{\mathrm{b},\beta})$. Critically, the hyperdistributions are unimodal with highest-density regions located some distance from the distribution edges, indicating the HMC sampling has converged well. }}
    \label{fig:corner_params_1}
\end{figure*}

\begin{figure*}
    \includegraphics[width=0.7\textwidth]{{graham_density-A-C-3.0-0.05_pair_1}.png}
    \caption{\drafting{Same as \autoref{fig:corner_params_1}}}
    \label{fig:corner_params_2}
\end{figure*}

\begin{figure*}
    \includegraphics[width=0.7\textwidth]{{graham_density-A-C-3.0-0.05_pair_2}.png}
    \caption{\drafting{Same as \autoref{fig:corner_params_1}}}
    \label{fig:corner_params_3}
\end{figure*}

\begin{figure*}
    \includegraphics[width=0.7\textwidth]{{graham_density-A-C-3.0-0.05_posterior_pred_log10_proj_density_mean}.png}
    \caption{\drafting{Posterior predictive estimate for the core-S\'ersic fit. Darker shaded regions correspond to higher Bayesian Credible Intervals (BCIs). The observed data is overlaid, and seen to lie well within the 50\% BCI. }}
    \label{fig:postpred}
\end{figure*}

\begin{figure*}
    \includegraphics{compare_AC_gqs.png}
    \caption{\drafting{Comparing the latent parameters for different members of the same progenitor class. Here shown is those families part of the AC merger class. There is no significant difference in latent parameter values with increasing rperi. TODO do this same plot for each merger class.}}
    \label{fig:compareAC}
\end{figure*}
